### 2015-02-16 paper/exprs.tex
added note about difference with earlier models of borrow checker

>>>>

\subsubsection*{TODO Move this into a foot note or something}
Rust itself and earlier models of Patina used a dramatically different form
of loan tracking and borrow checking. A universal set of loans it kept and threaded
through the type checker. Each loan generates a set of paths that cannot be accessed
without violating a loan guarantee. The borrow checker would then make sure that
no path used was in that set of forbidden paths.

This structure does not lend itself to proofs, so we devised this alternate system.
The system we present below is syntax driven and, we think, easier to understand.
Since proving this system matches the original would run into the problem we tried
to avoid in the first place, we satisfied ourselves with testing the two implementations.
The original model and this model agree on all the tests used in the original model.
